### 2022-06-28 input/figdel.tex
lowering page number, still long way to go 23 over 20
major changes everywhere
reworkd figures so they dont overlap, added a figure about naive deletes

\begin{figure}
  \newcommand{\SCALE}{0.95}

@@

  \begin{center}
    \subfloat[Part A][\label{fig:delA}$a$ deletes its partition. It
      notifies all \processes that belong to its
      partition.]{\input{input/figdelA.tex}}
    \hspace{3pt}
    \subfloat[Part B][\label{fig:delB}$\delta$ stops as soon as it encounters
      another partition. $b$ answers with its partition.]{\input{input/figdelB.tex}}
  \end{center}
  \caption{\label{fig:del}Efficient removal of a partition using
    scoped broadast. $a$ eventually acknowledges that it belongs to $P_d$ with $\alpha_d^3$ echoing.}
\end{figure}

>>>>

\begin{figure}[t]
  \newcommand{\SCALE}{0.8}

  \newcommand\X{42pt}
  \newcommand\Y{-40pt}

  \thickmuskip=0mu
  \medmuskip=0mu
  \thinmuskip=0mu

  \newcommand\INVISIBLESPACING{1.6}
  \newcommand\ADD{\alpha}
  \newcommand\DEL{\delta}

  \newcommand{\OACK}{0.5} %% opacity of acknowledgement alpha messages

@@

  \begin{center}
    \subfloat[Part A][\label{fig:delA}$a$ deletes its partition. It
      notifies all \processes that belong to its
      partition.]{\input{input/figdelA.tex}}
    \hspace{3pt}
    \subfloat[Part B][\label{fig:delB}$\delta$ stops when it encounters
      another partition. $b$ answers with its partition.]{\input{input/figdelB.tex}}
    \hspace{3pt}
    \subfloat[Part C][\label{fig:delC}$a$ receives, delivers, and forwards the message $\alpha_d^3$.
      Every node belongs to $P_d$.]{\input{input/figdelC.tex}}
  \end{center}
  \caption{\label{fig:del}Efficient removal of a partition using
    scoped broadast.} % $a$ eventually acknowledges that it belongs to $P_d$ with $\alpha_d^3$ echoing.}
\end{figure}

### 2022-06-28 input/proposal.tex
reworkd figures so they dont overlap, added a figure about naive deletes

\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos]
  In addition to FB, a \process $x$ that receives but does not deliver
  a staleness notification $\delta_{s}$ sends back --~or echoes~-- its
  best up-to-date delivered message: $(\last D_x = \alpha_{s'}^d
  \wedge \delta_{s'} \not\in D_x \wedge d_x(\alpha_{s'}^d)\rightarrow
  r_{xy}(\delta_{s})) \implies r_{xy}(\delta_{s}) \rightarrow
  s_{xy}(\alpha_{s'}^d\oplus^{w_{xy}})$.

  % $r_{xy}(\alpha_s)
  % \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'}^d\oplus
  % ^{w_{xy}})$ with $\alpha_{s'^d} = \min D_x \wedge \delta_{s'} \not\in
  % D_x$. \TODO{Rework min}
\end{definition}

Figure~\ref{fig:del} illustrates the behavior of this implementation
($\textup{FB}^+ \wedge \textup{FS}$).  Two partitions initially exist:
$P_a$ and $P_d$ that respectively include $\{a\}$, and $\{b, c,
d\}$. In Figure~\ref{fig:delA}, $a$ deletes its partition. FS in
Definition~\ref{def:fs} states that $a$ must notify all its
neighbors~--~here only $b$~-- that may belong to its partition.  In
Figure~\ref{fig:delB}, $b$ receives but does not deliver $\delta_a$
since $\delta_a$ does not target its current partition $P_d$.
$\textup{FB}^+$ in Definition~\ref{def:fbplus} states that $b$ must
echo back its own best up-to-date message $\alpha_d^3$, for it may be
the best for $a$. Eventually, every \process belongs to Partition
$P_d$. In this scenario, they reach consistent
partitioning. Unfortunately, this protocol does not ensure consistent
partitioning in every scenario.

>>>>

\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos]
  In addition to FB, a \process $x$ that receives but does not deliver
  a staleness notification $\delta_{s}$ replies by --~or echoes~-- its
  best up-to-date delivered message: $(\last D_x = \alpha_{s'}^d
  \wedge \delta_{s'} \not\in D_x \wedge d_x(\alpha_{s'}^d)\rightarrow
  r_{xy}(\delta_{s})) \implies r_{xy}(\delta_{s}) \rightarrow
  s_{xy}(\alpha_{s'}^d\oplus^{w_{xy}})$.
\end{definition}

Figure~\ref{fig:del} illustrates the behavior of this implementation
($\textup{FB}^+ \wedge \textup{FS}$).  Two partitions initially exist:
$P_a$ and $P_d$ that respectively include $\{a\}$, and $\{b, c,
d\}$. In Figure~\ref{fig:delA}, $a$ deletes its partition. FS in
Definition~\ref{def:fs} states that $a$ must notify all its
neighbors~--~here only $b$~-- that may belong to its partition.  In
Figure~\ref{fig:delB}, $b$ receives but does not deliver $\delta_a$
since $\delta_a$ does not target its current partition $P_d$.
$\textup{FB}^+$ in Definition~\ref{def:fbplus} states that $b$ must
echo back its own best up-to-date message $\alpha_d^3$, for it may be
the best for $a$. Figure~\ref{fig:delC} shows that every \process eventually belongs to 
$P_d$, therefore reaching consistent
partitioning. Unfortunately, this protocol does not ensure consistent
partitioning in every scenario.
